### 2018-08-23 doc/paper.tex
Making figure and equation numbering specific to section.
Adding Per as co-author.
Also removing the last sentence of the abstract. It was there in the
disseration as a way to flow into the discussion of compensated
algorithms for curve intersection, but here that isn't the focus.
Fixing first part of Introduction to be fluid.
It had two disjoint sections just pasted next to each other.

Also

- Making the introduction subsections into actual subsections
  rather than subsubsections
- Moving the "Bezier Intersection Problems" section to the appendix
- Adding a missing period after R^2 in a sen

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{High-order Solution Transfer between Curved Meshes}
\rhead{Danny Hermes}

%% H/T: https://tex.stackexchange.com/a/202047/32270
%%      https://tex.stackexchange.com/a/32463/32270
\usepackage[labelfont=bf]{caption}

@@

\begin{abstract}
\noindent The problem of solution transfer between meshes arises frequently in
computational physics, e.g. in Lagrangian methods where remeshing
occurs. The interpolation process must be conservative, i.e. it
must conserve physical properties, such as mass. We extend previous
works --- which described the solution transfer process for straight sided
unstructured meshes --- by considering high-order isoparametric meshes
with curved elements. The implementation is highly reliant on accurate
computational geometry routines for evaluating points on and
intersecting B\'{e}zier curves and triangles.
\\ \\
\noindent \emph{Keywords}: Remapping, Curved Meshes, Lagrangian,
Solution Transfer, Numerical analysis
\end{abstract}

@@

The first part is a general-purpose tool for computational physics problems.
The tool enables solution transfer across two curved meshes.
Since the tool requires a significant amount of computational geometry, the
second half focuses on computational geometry. In particular, it considers
cases where the geometric methods used have seriously degraded accuracy due to
ill-conditioning.

In computational physics, the problem of solution transfer between meshes
occurs in several applications. For example, by allowing the underyling
computational domain to change during a simulation, computational
effort can be focused dynamically to resolve sensitive features
of a numerical solution. Mesh adaptivity (see, for example,
\cite{Babuska1978, Peraire1987, Pain2001}), this in-flight change in the mesh,
requires translating the numerical solution from the old mesh to the new,
i.e. solution transfer. As another example, Lagrangian or particle-based
methods treat each node in the mesh as a particle and so with each timestep the
mesh travels \emph{with} the fluid (see, for example, \cite{Hirt1974}).
However, over (typically limited) time the mesh
becomes distorted and suffers a loss in element quality which causes
catastrophic loss in the accuracy of computation. To overcome this, the
domain must be remeshed or rezoned and the solution must be
transferred (remapped) onto the new mesh configuration.

When pointwise interpolation is used to transfer a solution, quantities with
physical meaning (e.g. mass, concentration, energy) may not be conserved.
To address this, there have been many explorations (for example,
\cite{Jiao2004, Farrell2009, Farrell2011}) of
\emph{conservative interpolation} (typically using Galerkin or
\(L_2\)-minimizing methods). In this work, the author introduces a
conservative interpolation method for solution transfer between high-order
meshes. These high-order meshes are typically curved, but not necessarily
all elements or at all timesteps.

The existing work on solution transfer has considered straight sided meshes,
which use shape functions that have degree \(p = 1\) to represent solutions
on each element or so-called superparametric elements (i.e. a linear mesh
with degree \(p > 1\) shape functions on a regular grid of points).
However, both to allow for greater geometric flexibility
and for high order of convergence, this work will consider the case
of curved isoparametric\footnote{I.e. the degree of the discrete field on the
mesh is same as the degree of the shape functions that determine the
mesh.} meshes. Allowing curved geometries is useful since many practical
problems involve geometries that change over time, such as flapping flight
or fluid-structure interactions. In addition, high-order CFD methods
(\cite{Wang2013}) have the ability to produce highly accurate solutions
with low dissipation and low dispersion error.

\subsection{Actual Intro}

In this chapter, an algorithm for conservative solution transfer between curved
meshes will be described. This has practical applications to many methods in
computational physics. Solution transfer is needed when a solution
(approximated by a discrete field) is known on a \emph{donor} mesh and must
be transferred to a \emph{target} mesh. In many applications, the field
must be conserved for physical reasons, e.g. mass or energy cannot leave or
enter the system, hence the focus on \emph{conservative} solution transfer.
A few scenarios where solution transfer is necessary will be considered below
to motivate the ``black box'' solution transfer algorithm.

Since solution transfer is so commonly needed in physical applications, this
problem of conservative interpolation has been considered already for
straight sided meshes. The \emph{common refinement} approach in
\cite{Jiao2004} is used to compare several methods for solution transfer across
two meshes. However, the problem of constructing a common refinement is
not discussed there. The problem of constructing such a refinement is
considered in \cite{Farrell2009, Farrell2011} (called a supermesh by
the authors).
However, the solution transfer becomes considerably more challenging for curved
meshes. For a sense of the difference between the straight sided and curved
cases, consider the problem of intersecting an element from the donor mesh
with an element from the target mesh. If the elements are triangles, the
intersection is either a convex polygon or has measure zero. If the elements
are curved, the intersection can be non-convex and can even split into
multiple disjoint regions.

\subsubsection{Lagrangian Methods}

@@

\subsubsection{Remeshing and Adaptivity}

@@

\subsubsection{High-order Meshes}

@@

\subsubsection{Multiphysics and Comparing Methods}

@@

\subsubsection{Local versus Global Transfer}

@@

\subsubsection{Limitations}

@@

The method described in this work only applies to meshes in \(\reals^2\).
Application to meshes in \(\reals^3\) is a direction for future research,
though the geometric kernels (see Chapter~\ref{sec:bezier-intersection})
become significantly more challenging to describe and implement. In
addition, the method will assume that every element in the
target mesh is contained in the donor mesh. This ensures that the solution
transfer is \emph{interpolation}. In the case where all target elements are
partially covered, \emph{extrapolation} could be used to extend a solution
outside the domain, but for totally uncovered elements there is no clear
correspondence to elements in the donor mesh.

@@

This work is organized as follows. Section~\ref{sec:preliminaries}
establishes common notation and reviews basic results relevant to the
topics at hand. Section~\ref{sec:bezier-intersection} is an
in-depth discussion of the computational geometry methods needed
to implement to enable solution transfer. Section~\ref{sec:galerkin-projection}
(and following)
describes the solution transfer process and gives results of some
numerical experiments confirming the rate of convergence.

@@

The problem of intersecting two B\'{e}zier curves is a core building
block for intersecting two B\'{e}zier triangles in \(\reals^2\)
Since a curve is an algebraic variety of dimension one,
the intersections will either be a curve segment common to both curves (if
they coincide) or a finite set of points (i.e. dimension zero).
Many algorithms have been described in the literature, both
geometric (\cite{Sederberg1986, Sederberg1990, Kim1998}) and
algebraic (\cite{Manocha:CSD-92-698}).

In the implementation for this work, the B\'{e}zier subdivision
algorithm is used.
In the case of a transversal intersection (i.e. one where the
tangents to each curve are not parallel and both are non-zero),
this algorithm performs very well. However, when curves are tangent,
a large number of (false) candidate intersections are detected and
convergence of Newton's method slows once in a neighborhood of an
actual intersection. Non-transversal intersections
have infinite condition number, but transversal intersections with
very high condition number can also cause convergence problems.

@@

This work has described a method for conservative interpolation
between curved meshes. The transfer process conserves globally
to machine precision since we can use exact quadratures for all
integrals. The primary source of error comes from solving the linear
system with the mass matrix for the target mesh. This allows
less restrictive usage of mesh adaptivity, which can make computations
more efficient. Additionally, having a global transfer algorithm
allows for remeshing to be done less frequently.

@@

>>>>

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{High-order Solution Transfer between Curved Meshes}
\rhead{Danny Hermes, Per-Olof Persson}

%% H/T: https://tex.stackexchange.com/a/28334/32270
\usepackage{chngcntr}
\counterwithin{figure}{section}
\counterwithin{equation}{section}
%% H/T: https://tex.stackexchange.com/a/202047/32270
%%      https://tex.stackexchange.com/a/32463/32270
\usepackage[labelfont=bf]{caption}

@@

\begin{abstract}
\noindent The problem of solution transfer between meshes arises frequently in
computational physics, e.g. in Lagrangian methods where remeshing
occurs. The interpolation process must be conservative, i.e. it
must conserve physical properties, such as mass. We extend previous
works --- which described the solution transfer process for straight sided
unstructured meshes --- by considering high-order isoparametric meshes
with curved elements.
\\ \\
\noindent \emph{Keywords}: Remapping, Curved Meshes, Lagrangian,
Solution Transfer, Numerical analysis
\end{abstract}

@@

In this paper, an algorithm for conservative solution transfer between curved
meshes will be described. This has practical applications to many methods in
computational physics. For example, by allowing the underyling
computational domain to change during a simulation, computational
effort can be focused dynamically to resolve sensitive features
of a numerical solution. Mesh adaptivity, this in-flight change in the mesh,
requires translating the numerical solution from the old mesh to the new,
i.e. solution transfer. As another example, Lagrangian or particle-based
methods treat each node in the mesh as a particle and so with each timestep the
mesh travels \emph{with} the fluid.
However, over (typically limited) time the mesh
becomes distorted and suffers a loss in element quality which causes
catastrophic loss in the accuracy of computation. To overcome this, the
domain must be remeshed or rezoned and the solution must be
transferred (remapped) onto the new mesh configuration. A few scenarios
where solution transfer is necessary will be considered below
to motivate the ``black box'' solution transfer algorithm.

Solution transfer is needed when a solution
(approximated by a discrete field) is known on a \emph{donor} mesh and must
be transferred to a \emph{target} mesh. In many applications, the field
must be conserved for physical reasons, e.g. mass or energy cannot leave or
enter the system, hence the focus on \emph{conservative} solution transfer
(typically using Galerkin or \(L_2\)-minimizing methods).

When pointwise interpolation is used to transfer a solution, quantities with
physical meaning (e.g. mass, concentration, energy) may not be conserved.
To address this, there have been many explorations of
\emph{conservative interpolation}. Since solution transfer is so commonly
needed in physical applications, this problem of conservative interpolation
has been considered already for straight sided meshes.
However, both to allow for greater
geometric flexibility and for high order of convergence, this paper will
consider the case of curved isoparametric\footnote{I.e. the degree of the
discrete field on the mesh is same as the degree of the shape functions that
determine the mesh.} meshes. Allowing curved geometries is useful since
many practical
problems involve geometries that change over time, such as flapping flight
or fluid-structure interactions. In addition, high-order CFD methods
have the ability to produce highly accurate solutions
with low dissipation and low dispersion error.

The \emph{common refinement} approach in
\cite{Jiao2004} is used to compare several methods for solution transfer across
two meshes. However, the problem of constructing a common refinement is
not discussed there. The problem of constructing such a refinement is
considered in \cite{Farrell2009, Farrell2011} (called a supermesh by
the authors).
However, the solution transfer becomes considerably more challenging for curved
meshes. For a sense of the difference between the straight sided and curved
cases, consider the problem of intersecting an element from the donor mesh
with an element from the target mesh. If the elements are triangles, the
intersection is either a convex polygon or has measure zero. If the elements
are curved, the intersection can be non-convex and can even split into
multiple disjoint regions.

\subsection{Lagrangian Methods}

@@

\subsection{Remeshing and Adaptivity}

@@

\subsection{High-order Meshes}

@@

\subsection{Multiphysics and Comparing Methods}

@@

\subsection{Local versus Global Transfer}

@@

\subsection{Limitations}

@@

The method described in this paper only applies to meshes in \(\reals^2\).
Application to meshes in \(\reals^3\) is a direction for future research,
though the geometric kernels (see Chapter~\ref{sec:bezier-intersection})
become significantly more challenging to describe and implement. In
addition, the method will assume that every element in the
target mesh is contained in the donor mesh. This ensures that the solution
transfer is \emph{interpolation}. In the case where all target elements are
partially covered, \emph{extrapolation} could be used to extend a solution
outside the domain, but for totally uncovered elements there is no clear
correspondence to elements in the donor mesh.

@@

This paper is organized as follows. Section~\ref{sec:preliminaries}
establishes common notation and reviews basic results relevant to the
topics at hand. Section~\ref{sec:bezier-intersection} is an
in-depth discussion of the computational geometry methods needed
to implement to enable solution transfer. Section~\ref{sec:galerkin-projection}
(and following)
describes the solution transfer process and gives results of some
numerical experiments confirming the rate of convergence.

@@

@@

This paper has described a method for conservative interpolation
between curved meshes. The transfer process conserves globally
to machine precision since we can use exact quadratures for all
integrals. The primary source of error comes from solving the linear
system with the mass matrix for the target mesh. This allows
less restrictive usage of mesh adaptivity, which can make computations
more efficient. Additionally, having a global transfer algorithm
allows for remeshing to be done less frequently.

@@

The problem of intersecting two B\'{e}zier curves is a core building
block for intersecting two B\'{e}zier triangles in \(\reals^2\).
Since a curve is an algebraic variety of dimension one,
the intersections will either be a curve segment common to both curves (if
they coincide) or a finite set of points (i.e. dimension zero).
Many algorithms have been described in the literature, both
geometric (\cite{Sederberg1986, Sederberg1990, Kim1998}) and
algebraic (\cite{Manocha:CSD-92-698}).

In the implementation for this paper, the B\'{e}zier subdivision
algorithm is used.
In the case of a transversal intersection (i.e. one where the
tangents to each curve are not parallel and both are non-zero),
this algorithm performs very well. However, when curves are tangent,
a large number of (false) candidate intersections are detected and
convergence of Newton's method slows once in a neighborhood of an
actual intersection. Non-transversal intersections
have infinite condition number, but transversal intersections with
very high condition number can also cause convergence problems.
